Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A

### 2017-05-15 draft.tex
lots of small changes.

%-- bremsstrahlung--	
\subsection{bremsstrahlung of $\Aprime$ Bosons}

@@

The eight diagrams contribute the following eight terms to the pp amplitude, 
%
\begin{widetext}
\begin{eqnarray}
	M_1 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\ 
	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
	M_2 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\  
	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
	M_3 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
	M_4 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
	M_5 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\
	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_1),\\
	M_6 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\ 
	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
	M_7 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_2),\\
	M_8 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
\end{eqnarray}
\end{widetext}
%
where the dark photon polarization is given by $\epsilon^{\nu}$. These expressions are identical to those 
given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
Our result contains over 200 terms, so we do not reproduce it here for reasons of convenience. However, we note that our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.

The pn process contains four diagrams analogous to the the diagrams for the pp process (only four, of course, 
because the neutrons cannot radiate the $\Aprime$). The new diagram that is relevant in the pn process is shown in 
Fig.~\ref{fig:npdiagram} and yields a contribution of 
%
\begin{widetext}
\begin{equation}
M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \epsilon.
\end{equation}
\end{widetext}
%
The pn processes likewise yields a squared amplitude, 
$\vert \mathcal{M}_{\mathrm{pn}} \vert^2$ that is unwieldy, so we do not give the 
the full expression here. We provide mathematica notebooks detailing our 
computation of the amplitudes with this submission.

@@

To obtain the dark gauge boson luminosity from $Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, 
we assumed that $\Aprime$ production takes place in a stellar core of radius $\sim 1$~km, 
so that the total luminosity of $\Aprime$ is 
%
\begin{equation}
L_{\mathrm{A}'} = V (Q_{\mathrm{pp}} + Q_{\mathrm{pn}}),
\end{equation}
%
where $V$ is the volume of the sphere, and the luminosity per unit mass within the core is 
%
\begin{equation}
\left( \frac{L_{\mathrm{A'}}}{M} \right) = \frac{Q_{\mathrm{pp}} + Q_{\mathrm{pn}}}{\rho}, 
\end{equation}
%
where $\rho = 3 \times 10^{14}\, \mathrm{g/cm}^3$ is the mass density of the core\footnote{
We use the symbol $\left( L_{\mathrm{A'}}/M \right)$ for the luminosity per unit mass rather than 
the more conventional symbol $\epsilon_{\mathrm{A'}}$ in order to avoid confusion with the 
mixing parameter $\varepsilon$.}. Following previous studies, the energy loss rate into novel 
particles cannot exceed 
%
\begin{equation}
\left( \frac{L_{\mathrm{max}}}{M} \right) \approx 10^{19} \, \frac{\mathrm{erg}}{\mathrm{g}\cdot \mathrm{s}}
\end{equation}
%
without significantly reducing the duration of the neutrino burst observed at Earth for SN1987A 
\cite{raffelt96_book}. Writing $(L_{\mathrm{A'}}/M) = \varepsilon^2 I_{\mathrm{A'}}(m_{\mathrm{A'}},T)$, 
we delineate the constraint on the dark photon mixing parameter by 
%
\begin{equation}
\label{eq:bound1}
\varepsilon \lesssim \sqrt{\frac{(L_{\mathrm{max}}/M)}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
\end{equation}
%
At this point, we note that Dent et al. in Ref.~\cite{dent_etal12} took a value of 
$(L_{\mathrm{max}}/M)$ approximately three orders of magnitude larger than 
this accepted value. Remarkably, this nearly canceled the errors in their evaluation of 
$Q_{\mathrm{pp}}$ and $Q_{\mathrm{np}}$ so that they quote constraints that are 
within an order of magnitude of the correct result.

@@

The dark boson has a typical lifetime of
\begin{equation}
\tau_{\mathrm{A}'} = \frac{3}{\varepsilon^2 \alpha m_{\mathrm{A}'}},
\end{equation}
where $\alpha$ is the fine structure constant. Therefore,
the typical travel distance to decay is given by 
%
\beq
\label{eq:decaylength}
l = \beta \tau_{\mathrm{A}'} = \frac{3 q_{\mathrm{A}'}}{\varepsilon^2 \alpha m_{\mathrm{A}'}^2},
\eeq
and so the fraction escaping the supernova before decaying may be estimated as (e.g., Ref.~\cite{bjorken_etal09})
\beq
\label{eq:decayfactor}
\exp \left( - \frac{r_{\mathrm{decay}}}{l} \right) = 
\exp \left( - \frac{r_{\mathrm{decay}} m_{\mathrm{A'}}^2\alpha \varepsilon^2}{3 q_{\mathrm{A'}}} \right),
\eeq
%
where $r_\mathrm{decay}$ is chosen to be 10 km, since the density of the supernova drops quickly around that size. This approximation should be valid so long as the size of the supernova within which standard model decay products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, an assumption which should be satisfied comfortably. To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds as in the previous subsection. The limit is derived in the same way, with the additional complication that $I_{\mathrm{A}'}$ is now a function of $\varepsilon $, in addition to $m_{\mathrm{A}'}$ and $T$. The constraint Eq.~(\ref{eq:bound1}), therefore, becomes a transcendental equation that must be solved numerically.

@@

The inverse mean free path can be obtained by modifying $ Q_i $, 
the expression for the energy loss rate, as follows: removing the factor of $ E_\mathrm{A'} $ 
and the phase space integral over $ \qa $, and adding a factor of $ e^{E_\mathrm{A'}/T} $ for detailed balance. 
\arz{I'm not sure that I follow this somewhat cavalier statement about detailed balance. Can someone 
please explain this to me when we meet. In my earlier rounds of thinking about this, I took that factor 
at face value as given, assuming I'd eventually be able to figure out where it comes from.} 
This gives the inverse mean free path as a function of mass and coupling. 
Again, we perform the required integration numerically using the {\tt CUBA }package. 
This then allows the calculation of $\kappa_{\mathrm{pp}}$ and $\kappa_{\mathrm{pn}}$, 
which are the opacities due to inverse bremsstrahlung for proton-proton and proton-neutron 
processes respectively. These dominate the opacity of the star to $A'$ propagation. 
The inverse opacities for the $pn$ and $pp$ processes add, 
giving the total opacity $ \kappa^{-1} = \kappa_{\mathrm{pp}}^{-1} + \kappa_{\mathrm{pn}}^{-1} $

@@

Rrapaj and Reddy \cite{rrapaj_reddy16} estimated $A'$ luminosity 
using the SRA for nucleon interactions, which enabled them to use 
nuclear scattering data in the estimation of the bremsstrahlung rate. 
This approach overcomes the shortcomings of the OPE approximation, 
though at high dark photon masses this approximation breaks down. 
We have repeated the calculation in the SRA as described in 
Rrapaj and Reddy \cite{rrapaj_reddy16} and our result is 
shown as the purple line in Fig.~\ref{fig:constraint}. 
Our SRA result is in excellent agreement with Ref.~\cite{rrapaj_reddy16}. It is 
also worth noting that the SRA and OPE approximations yield constraints 
on $\varepsilon$ that agree quite well with each other. This suggests, of course, 
that the discrepancy between Ref.~\cite{dent_etal12} and Ref.~\cite{rrapaj_reddy16} 
stems primarily from errors in Ref.~\cite{dent_etal12} and not to the OPE model 
of nucleon interactions. In an effort to estimate 
the possible shortcomings of the SRA approximation, the green line in 
Fig.~\ref{fig:constraint} shows the lower bound on the excluded region that 
we drive using the SRA along with OPE expressions for nucleon scattering 
cross sections. As one can see, the SRA is in good agreement with the full 
OPE bound. Consequently, we suggest that use of the SRA in this context 
results in an overestimate of the lower limit on $\varepsilon$ of less than 
a factor or three.

>>>>

%-- bremsstrahlung--	
\subsection{Bremsstrahlung of $\Aprime$ Bosons}

@@

The eight diagrams contribute the following eight terms to the pp amplitude, 
%
\begin{widetext}
\begin{eqnarray}
	M_1 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\ 
	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_{\mathrm N})\slashed \epsilon  u(p_1), \\
	M_2 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_1}\  
	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_{\mathrm N})\slashed{\epsilon} u(p_1),\\
	M_3 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_{\mathrm N})\slashed \epsilon  u(p_2), \\
	M_4 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 - 2 \qa \cdot p_2}\ 
	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_{\mathrm N})\slashed \epsilon  u(p_2), \\
	M_5 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\
	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_{\mathrm N})\gamma_5 u(p_1),\\
	M_6 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_3}\ 
	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_{\mathrm N})\gamma_5 u(p_2),\\
	M_7 &=& \frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_{\mathrm N})\gamma_5 u(p_2),\\
	M_8 &=& -\frac{4 M_{\mathrm N}^2}{ m_\pi^2} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{\mathrm{\Aprime}}^2 + 2 \qa \cdot p_4}\ 
	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_{\mathrm N})\gamma_5 u(p_1),
\end{eqnarray}
\end{widetext}
%
where the dark photon polarization is given by $\epsilon^{\nu}$. These expressions are identical to those 
given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
Our squared matrix element contains over 200 terms, so we do not reproduce it here for reasons of convenience. However, we note that our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.

The pn process contains four diagrams analogous to the diagrams for the pp process (only four, of course, 
because the neutrons cannot radiate the $\Aprime$). The new diagram that is relevant in the pn process is shown in 
Fig.~\ref{fig:npdiagram} and yields a contribution of 
%
\begin{widetext}
\begin{equation}
M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \epsilon.
\end{equation}
\end{widetext}
%
The pn processes likewise yields a squared amplitude, 
$\vert \mathcal{M}_{\mathrm{pn}} \vert^2$ that is unwieldy, so we do not give the 
the full expression here. We provide mathematica notebooks detailing our 
computation of the amplitudes with this submission.

@@

To obtain the dark gauge boson luminosity from $Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, 
we assumed that $\Aprime$ production takes place in a stellar core of radius $\sim 1$~km, 
so that the total luminosity of $\Aprime$ is 
%
\begin{equation}
L_{\mathrm{A}'} = V (Q_{\mathrm{pp}} + Q_{\mathrm{pn}}),
\end{equation}
%
where $V$ is the volume of the sphere, and the luminosity per unit mass within the core is 
%
\begin{equation}
\left( \frac{L_{\mathrm{A'}}}{M} \right) = \frac{Q_{\mathrm{pp}} + Q_{\mathrm{pn}}}{\rho}, 
\end{equation}
%
where $\rho = 3 \times 10^{14}\, \mathrm{g/cm}^3$ is the mass density of the core\footnote{
We use the symbol $\left( L_{\mathrm{A'}}/M \right)$ for the luminosity per unit mass rather than 
the more conventional symbol $\epsilon_{\mathrm{A'}}$ in order to avoid confusion with the 
mixing parameter $\varepsilon$.}. Following previous studies, the energy loss rate into novel 
particles cannot exceed 
%
\begin{equation}
\left( \frac{L_{\mathrm{max}}}{M} \right) \approx 10^{19} \, \frac{\mathrm{erg}}{\mathrm{g}\cdot \mathrm{s}}
\end{equation}
%
without significantly reducing the duration of the neutrino burst observed at Earth for SN1987A 
\cite{raffelt96_book}. Writing $(L_{\mathrm{A'}}/M) = \varepsilon^2 I_{\mathrm{A'}}(m_{\mathrm{A'}},T)$, 
we delineate the constraint on the dark photon mixing parameter by 
%
\begin{equation}
\label{eq:bound1}
\varepsilon \lesssim \sqrt{\frac{(L_{\mathrm{max}}/M)}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
\end{equation}
%
At this point, we note that Dent et al. in Ref.~\cite{dent_etal12} took a value of 
$(L_{\mathrm{max}}/M)$ approximately three orders of magnitude larger than 
this accepted value. Remarkably, this nearly canceled the errors in their evaluation of 
$Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$ so that they quote constraints that are 
within an order of magnitude of the correct result.

@@

The dark boson has a typical lifetime of
\begin{equation}
\tau_{\mathrm{A}'} = \frac{3}{\varepsilon^2 \alpha m_{\mathrm{A}'}},
\end{equation}
where $\alpha$ is the fine structure constant. Therefore,
the typical travel distance to decay is given by 
%
\beq
\label{eq:decaylength}
l = \beta \tau_{\mathrm{A}'} = \frac{3 q_{\mathrm{A}'}}{\varepsilon^2 \alpha m_{\mathrm{A}'}^2},
\eeq
and so the fraction escaping the supernova before decaying may be estimated as (e.g., Ref.~\cite{bjorken_etal09})
\beq
\label{eq:decayfactor}
\exp \left( - \frac{r_{\mathrm{decay}}}{l} \right) = 
\exp \left( - \frac{r_{\mathrm{decay}} m_{\mathrm{A'}}^2\alpha \varepsilon^2}{3 q_{\mathrm{A'}}} \right),
\eeq
%
where $r_\mathrm{decay}$ is chosen to be 10 km, since the density of the supernova drops quickly around that size. This approximation should be valid so long as the size of the supernova within which standard model decay products can interact and be thermalized is significantly larger than the region within which $\Aprime$ are produced, an assumption that should be satisfied comfortably. To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds as in the previous subsection. The limit is derived in the same way, with the additional complication that $I_{\mathrm{A}'}$ is now a function of $\varepsilon $, in addition to $m_{\mathrm{A}'}$ and $T$. The constraint Eq.~(\ref{eq:bound1}), therefore, becomes a transcendental equation that must be solved numerically.

@@

The inverse mean free path can be obtained by modifying $ Q_i $, 
the expression for the energy loss rate, as follows: removing the factor of $ E_\mathrm{A'} $ 
and the phase space integral over $ \qa $, and adding a factor of $ e^{E_\mathrm{A'}/T} $ for detailed balance. 
\arz{I'm not sure that I follow this somewhat cavalier statement about detailed balance. Can someone 
please explain this to me when we meet. In my earlier rounds of thinking about this, I took that factor 
at face value as given, assuming I'd eventually be able to figure out where it comes from.} 
This gives the inverse mean free path as a function of mass and coupling. 
Again, we perform the required integration numerically using the {\tt CUBA }package. 
This then allows the calculation of $\kappa_{\mathrm{pp}}$ and $\kappa_{\mathrm{pn}}$, 
which are the opacities due to inverse bremsstrahlung for proton-proton and proton-neutron 
processes respectively. These dominate the opacity of the star to $\mathrm{A'}$ propagation. 
The inverse opacities for the $\mathrm{pn}$ and $\mathrm{pp}$ processes add, 
giving the total opacity $ \kappa^{-1} = \kappa_{\mathrm{pp}}^{-1} + \kappa_{\mathrm{pn}}^{-1} $

@@

Rrapaj and Reddy \cite{rrapaj_reddy16} estimated $\mathrm{A'}$ luminosity 
using the SRA for nucleon interactions, which enabled them to use 
nuclear scattering data in the estimation of the bremsstrahlung rate. 
This approach overcomes the shortcomings of the OPE approximation, 
though at high dark photon masses this approximation breaks down. 
We have repeated the calculation in the SRA as described in 
Rrapaj and Reddy \cite{rrapaj_reddy16} and our result is 
shown as the purple line in Fig.~\ref{fig:constraint}. 
Our SRA result is in excellent agreement with Ref.~\cite{rrapaj_reddy16}. It is 
also worth noting that the SRA and OPE approximations yield constraints 
on $\varepsilon$ that agree quite well with each other. This suggests, of course, 
that the discrepancy between Ref.~\cite{dent_etal12} and Ref.~\cite{rrapaj_reddy16} 
stems primarily from errors in Ref.~\cite{dent_etal12} and not to the OPE model 
of nucleon interactions. In an effort to estimate 
the possible shortcomings of the SRA approximation, the green line in 
Fig.~\ref{fig:constraint} shows the lower bound on the excluded region that 
we drive using the SRA along with OPE expressions for nucleon scattering 
cross sections. As one can see, the SRA is in good agreement with the full 
OPE bound. Consequently, we suggest that use of the SRA in this context 
results in an overestimate of the lower limit on $\varepsilon$ of less than 
a factor or three.
